\tealeaves: an R package for modelling leaf temperature using energy budgets

### 2019-07-26 ms/ms.Rnw
added Zenodo DOI

Annotated source code to generate this manuscript is available on GitHub (https://github.com/cdmuir/tealeaves-ms) and archived on Zenodo (https://doi.org/10.5281/zenodo.XXXXXX). A development version of \tealeaves~is currently available on GitHub (https://github.com/cdmuir/tealeaves) and the version used for this manuscript is archived on Zenodo (https://doi.org/10.5281/zenodo.2808079).

>>>>

Annotated source code to generate this manuscript is available on GitHub (https://github.com/cdmuir/tealeaves-ms) and archived on Zenodo (https://doi.org/10.5281/zenodo.167281492). A development version of \tealeaves~is currently available on GitHub (https://github.com/cdmuir/tealeaves) and the version used for this manuscript is archived on Zenodo (https://doi.org/10.5281/zenodo.2808079).
